An assessment of the biodiversity - ecosystem function relationship in southern African woodlands

### 2019-12-16 include/clust_summ.tex
Updated manuscript

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Dec 12, 2019 - 12:06:51
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust4 & c\_dom & c\_ind & n\_plots & n\_species\_raref & stems\_ha & agb\_ha \\ 
\hline \\[-1.8ex] 
1 & Julbernadia spp., Brachystegia spiciformis, Baikeaea plurijuga & Diplorhynchus condylocarpon, Burkea africana, Pseudolachnostylis maprouneifolia & 679 & 11(11.1) & 172(148) & 37.6(34.88) \\ 
2 & Julbernadia spp., Brachystegia spp., Isoberlinia angolensis & Julbernardia paniculata, Isoberlinia angolensis, Brachystegia longifolia & 746 & 18(17.5) & 216(170) & 49.1(43.34) \\ 
3 & Spirostachys africana, Senegalia spp., Euclea racemosa & Baikiaea plurijuga, Senegalia ataxacantha, Combretum collinum & 225 & 10(10) & 166(160) & 46.2(47.82) \\ 
4 & Colophospermum mopane & Colophospermum mopane, Combretum spp. & 99 & 7(8.2) & 190(155.7) & 41.5(36.93) \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Dec 16, 2019 - 11:33:55
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
clust4 & c\_dom & c\_ind & n\_plots & n\_species\_raref & stems\_ha & agb\_ha \\ 
\hline \\[-1.8ex] 
1 & Julbernadia spp., Brachystegia spiciformis, Baikeaea plurijuga & Diplorhynchus condylocarpon, Burkea africana, Pseudolachnostylis maprouneifolia & 687 & 11(11.2) & 170(145.3) & 37(34.68) \\ 
2 & Julbernadia spp., Brachystegia spp., Isoberlinia angolensis & Julbernardia paniculata, Isoberlinia angolensis, Brachystegia longifolia & 757 & 18(17.6) & 215(171.7) & 48.8(43.7) \\ 
3 & Spirostachys africana, Senegalia spp., Euclea racemosa & Baikiaea plurijuga, Senegalia ataxacantha, Combretum collinum & 226 & 10(10) & 165(157.5) & 46(47.81) \\ 
4 & Colophospermum mopane & Colophospermum mopane, Combretum spp. & 99 & 7(8.2) & 190(155.7) & 41.5(36.93) \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

### 2019-12-16 manuscript/include/clust_summ.tex
Updated manuscript

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Nov 20, 2019 - 20:22:20
\begin{table}[!htbp] \centering 
  \caption{Description of the biogeographical clusters (C1-C5) to which each plot in the study was assigned. Indicator species were generated using Dufrene-Legendre indicator species analysis \citep{Dufrene1997} implemented with \texttt{indval()} from the \texttt{labdsv} R package \citep{labdsv} and represent species which define the given cluster. Dominant species were identified by choosing the species with the largest AGB contribution within each cluster. Numeric values of species richness, stems ha\textsuperscript{-1} and AGB are medians and interquartile ranges.} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Dominant species} & {Indicator species} & {N plots} & {Species rich.} & {Stems ha\textsuperscript{-1}} & {AGB (t ha\textsuperscript{-1})} \\
\hline \\[-1.8ex] 
1 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernadia }spp. \\ \textit{Brachystegia spiciformis} \\ \textit{Baikeaea plurijuga} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Diplorhynchus condylocarpon} \\ \textit{Burkea africana} \\ \textit{Pseudolachnostylis maprouneifolia} \end{tabular} & 734 & 6(5) & 276(208) & 35.4(31.41) \\ 
\hline
2 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernadia }spp. \\ \textit{Brachystegia }spp. \\ \textit{Isoberlinia angolensis} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernardia paniculata} \\ \textit{Isoberlinia angolensis} \\ \textit{Brachystegia longifolia} \end{tabular} & 728 & 8(5) & 277(196.9) & 46.9(44.96) \\ 
\hline
3 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Spirostachys africana} \\ \textit{Senegalia }spp. \\ \textit{Euclea racemosa} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Baikiaea plurijuga} \\ \textit{Senegalia ataxacantha} \\ \textit{Combretum collinum} \end{tabular} & 299 & 9(8) & 410(427.7) & 46.6(43.51) \\ 
\hline
4 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \\ \textit{Combretum }spp. \end{tabular} & 102 & 4(4) & 322(228.8) & 43.8(36.49) \\ 
\hline
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Dec 16, 2019 - 11:33:55
\begin{table}[!htbp] \centering 
  \caption{Description of the biogeographical clusters (C1-C5) to which each plot in the study was assigned. Indicator species were generated using Dufrene-Legendre indicator species analysis \citep{Dufrene1997} implemented with \texttt{indval()} from the \texttt{labdsv} R package \citep{labdsv} and represent species which define the given cluster. Dominant species were identified by choosing the species with the largest AGB contribution within each cluster. Numeric values of species richness, stems ha\textsuperscript{-1} and AGB are medians and interquartile ranges (75th percentile - 25th percentile).} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Dominant species} & {Indicator species} & {N plots} & {Species rich.} & {Stems ha\textsuperscript{-1}} & {AGB (t ha\textsuperscript{-1})} \\
\hline \\[-1.8ex] 
1 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernadia }spp. \\ \textit{Brachystegia spiciformis} \\ \textit{Baikeaea plurijuga} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Diplorhynchus condylocarpon} \\ \textit{Burkea africana} \\ \textit{Pseudolachnostylis maprouneifolia} \end{tabular} & 687 & 11(11.2) & 170(145.3) & 37(34.68) \\ 
\hline
2 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernadia }spp. \\ \textit{Brachystegia }spp. \\ \textit{Isoberlinia angolensis} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Julbernardia paniculata} \\ \textit{Isoberlinia angolensis} \\ \textit{Brachystegia longifolia} \end{tabular} & 757 & 18(17.6) & 215(171.7) & 48.8(43.7) \\ 
\hline
3 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Spirostachys africana} \\ \textit{Senegalia }spp. \\ \textit{Euclea racemosa} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Baikiaea plurijuga} \\ \textit{Senegalia ataxacantha} \\ \textit{Combretum collinum} \end{tabular} & 226 & 10(10) & 165(157.5) & 46(47.81) \\ 
\hline
4 & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \\ \textit{Combretum }spp. \end{tabular} & 99 & 7(8.2) & 190(155.7) & 41.5(36.93) \\ 
\hline
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

### 2019-12-16 manuscript/include/data_clean_flow.tex
Updated manuscript

\tikzset{mystyle/.style={->,double=black}}
\node  [round] (a)                    {Exclude plots with:\\- Charcoal and timber  harvesting\\- Farming/grazing\\- Fire manipulation};
\node  [box] (b) [right = 1.2cm of a] {Aggregate values of Zambian\\forestry commission plots};
\node  [round] (c) [below = 1.2cm of b] {Exclude plots where minimum\\measured tree size \textgreater{}5 cm};
\node  [round] (d) [left = 1.2cm of c] {Exclude stems:\\- \textless{}5 cm DBH\\- Dead\\- Unknown species};
\node  [box] (e) [below = 1.2cm of d] {Calculate mean plot\\level woodland traits};
\node  [round] (f) [right = 1.2cm of e] {Exclude plots with no\\tree species diversity};
\node  [round] (g) [below = 1.2cm of f] {Exclude compositional\\outlier plots};
\node  [box] (h) [left = 1.2cm of g] {Calculate reversed\\variables for SEM};
\node  [box] (i) [below = 1.2cm of h] {Transform variables to\\achieve normality};
\node  [box] (j) [right = 1.2cm of i] {Standardize variables};
\node  [diam] (k) [below = 1.2cm of j] {Analysis};
\draw [path] (a) -> (b);
\draw [path] (b) -> (c);
\draw [path] (c) -> (d);
\draw [path] (d) -> (e);
\draw [path] (e) -> (f);
\draw [path] (f) -> (g);
\draw [path] (g) -> (h);
\draw [path] (h) -> (i);
\draw [path] (i) -> (j);
\draw [path] (j) -> (k);

>>>>

\tikzset{mystyle/.style={->,double=black}}
\node  [round] (a)                    {Exclude plots with:\\- Charcoal and timber  harvesting\\- Farming/grazing\\- Fire manipulation};
\node  [box] (b) [right = 1.2cm of a] {Aggregate values of Zambian\\forestry commission plots};
\node  [round] (c) [below = 1.2cm of b] {Exclude plots where minimum\\measured tree size \textgreater{}10 cm};
\node  [round] (d) [left = 1.2cm of c] {Exclude stems:\\- \textless{}10 cm DBH\\- Dead\\- Unknown species};
\node  [box] (e) [below = 1.2cm of d] {Calculate mean plot\\level woodland traits};
\node  [round] (f) [right = 1.2cm of e] {Exclude plots with no\\tree species diversity};
\node  [round] (g) [below = 1.2cm of f] {Exclude compositional\\outlier plots};
\node  [box] (h) [left = 1.2cm of g] {Calculate reversed\\variables for SEM};
\node  [box] (i) [below = 1.2cm of h] {Transform variables to\\achieve normality};
\node  [box] (j) [right = 1.2cm of i] {Standardize variables};
\node  [diam] (k) [below = 1.2cm of j] {Analysis};
\draw [path] (a) -> (b);
\draw [path] (b) -> (c);
\draw [path] (c) -> (d);
\draw [path] (d) -> (e);
\draw [path] (e) -> (f);
\draw [path] (f) -> (g);
\draw [path] (g) -> (h);
\draw [path] (h) -> (i);
\draw [path] (i) -> (j);
\draw [path] (j) -> (k);

### 2019-12-16 manuscript/include/struc_model_fit_clust_stats.tex
Part way through editing
A day of working with clust4
Draft sent to supervisor
Updated models
Updated manuscript

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Fri, Nov 08, 2019 - 17:15:20
\begin{table}[!htbp] \centering 
  \caption{Model fit statistics for SEMs investigating the effects of tree diversity and stem density on AGB (\autoref{struc_mod}).} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Params.} & {n} & {$\chi^{2}$} & {DoF} & {CFI} & {TLI} & {LogLik} & {AIC} & {RMSEA} & {SRMR} \\
\hline \\[-1.8ex] 
C1 & 12 & 420 & 10.430 & 3 & 0.987 & 0.958 & -2630.700 & 5285.300 & 0.080 & 0.029 \\ 
C2 & 12 & 671 & 50.320 & 3 & 0.942 & 0.806 & -3730.200 & 7484.300 & 0.150 & 0.052 \\ 
C3 & 12 & 105 & 24.970 & 3 & 0.880 & 0.601 & -619.100 & 1262.300 & 0.260 & 0.142 \\ 
C4 & 12 & 46 & 2.710 & 3 & 1 & 1.008 & -257.900 & 539.900 & 0 & 0.025 \\ 
C5 & 12 & 84 & 5.400 & 3 & 0.981 & 0.936 & -529.500 & 1083 & 0.100 & 0.085 \\ 
All & 12 & 1326 & 62.210 & 3 & 0.968 & 0.895 & -8110.500 & 16245 & 0.120 & 0.036 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mon, Dec 16, 2019 - 16:41:44
\begin{table}[!htbp] \centering 
  \caption{Model fit statistics for SEMs investigating the effects of tree diversity and stem density on AGB (\autoref{struc_mod}).} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {n} & {$\chi^{2}$} & {DoF} & {CFI} & {TLI} & {LogLik} & {RMSEA} & {$R^{2}$ AGB} \\
\hline \\[-1.8ex] 
Marginal miombo & 525 & 47.480 & 6 & 0.964 & 0.910 & -3730.100 & 0.110 & 0.730 \\ 
Core miombo & 668 & 59.440 & 6 & 0.958 & 0.895 & -4219 & 0.100 & 0.680 \\ 
Baikiaea & 47 & 5.860 & 6 & 0.998 & 0.994 & -323.100 & 0.030 & 0.720 \\ 
Mopane & 84 & 9.420 & 6 & 0.971 & 0.927 & -588.900 & 0.080 & 0.450 \\ 
All & 1324 & 82.020 & 6 & 0.973 & 0.932 & -9122.800 & 0.090 & 0.700 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
